### 2019-08-06 chapters/4-approach.tex
Add following interactions and traces examples
Add text about function container and argument container

The implementation stores these observations as entities called \textit{interactions}. As explained later in \secref{run-time-analysis}, they are used for translating, modifying and aggregating Jalangi's raw event information in order to get an application specific data representation.

@@

\subsection{Analysis} \label{run-time-analysis}
\todo{inputValue}
\input{figures/approach/run-time-information-gathering/analysis/input-value.tex}
\input{figures/approach/run-time-information-gathering/analysis/get-field.tex}
\input{figures/approach/run-time-information-gathering/analysis/method-call.tex}
\input{figures/approach/run-time-information-gathering/analysis/used-as-argument.tex}

\todo{getField}
\todo{putField}
\todo{methodCall}
\todo{usedAsArgument}
\todo{operatorInteraction}

\todo{followingInteractions}
\todo{traces}

>>>>

The implementation stores these observations as entities called \textit{interactions}. As explained later in \secref{sec:run-time-analysis}, they are used for translating, modifying and aggregating Jalangi's raw event information in order to get an application specific data representation.

@@

\subsection{Analysis} \label{sec:run-time-analysis}
The provided analysis module implements the following Jalangi callbacks, which were explained in detail in \secref{sec:jalangi}:
\begin{itemize}
  \item binaryPre()
  \item declare()
  \item getFieldPre()
  \item putFieldPre()
  \item functionEnter()
  \item functionExit()
  \item invokeFun()
  \item invokeFunPre()
  \item unaryPre()
  \item write()
\end{itemize}

They enable observation of all JS operations considered relevant. Every invoked function is given an unique identifier and information for each argument of every function gets stored. The entities \mintinline{bash}{FunctionContainer}, \mintinline{bash}{ArgumentContainer} and \mintinline{bash}{Interaction} are introduced to support the representation of the gathered run-time information.

Run-time information is stored in a map that contains objects of type \mintinline{bash}{FunctionContainer}.
This entity contains static information about the function as well as implementation specific data needed for generating the right type of declaration file, as explained in \secref{sec:declaration-files-background}. Each field of the entity is explained in \coderef{code:function-container}.

\begin{code}
  \jscode{code/run-time-information-gathering/analysis/function-container.js}
  \caption[FunctionContainer object]{\textbf{\mintinline{bash}{FunctionContainer} object} - \mintinline{bash}{FunctionContainer} is the main entity in the map where the run-time information gets gathered. It contains implementation specific information for the declaration files generation. Entities of type \mintinline{bash}{ArgumentContainer} get appended to the \mintinline{bash}{args} property.}
  \label{code:function-container}
\end{code}

Moreover, as explained in \coderef{code:argument-container}, the \mintinline{bash}{ArgumentContainer} object works as a container for all interactions recorded for that argument. Additionally, it contains simple information about the argument itself, like the index or the name given in the function declaration.

\begin{code}
  \jscode{code/run-time-information-gathering/analysis/argument-container.js}
  \caption[ArgumentContainer object]{\textbf{\mintinline{bash}{ArgumentContainer} object} - The \mintinline{bash}{ArgumentContainer} object works mainly as a container for all relevant observations regarding that argument.}
  \label{code:argument-container}
\end{code}

Finally, observations on the arguments of a function are stored as objects of type \mintinline{bash}{Interaction}. They have to be always associated to an \mintinline{bash}{ArgumentContainer} object or to another \mintinline{bash}{Interaction}. They are explained in detail in \secref{sec:run-time-interactions}.

\subsection{Interactions} \label{sec:run-time-interactions}

\draft{enables the developer to create custom analysis modules by implementing the callbacks to virtually every JavaScript. Jalangi provides a way of writing a custom analysis by implementing}

\subsubsection{\textit{inputValue} interaction}
\input{figures/approach/run-time-information-gathering/analysis/input-value.tex}

\subsubsection{\textit{getField} interaction}
\input{figures/approach/run-time-information-gathering/analysis/get-field.tex}

\subsubsection{\textit{methodCall} interaction}
\input{figures/approach/run-time-information-gathering/analysis/method-call.tex}

\subsubsection{\textit{usedAsArgument} interaction}
\input{figures/approach/run-time-information-gathering/analysis/used-as-argument.tex}

\subsubsection{\textit{operator} interaction}

\subsubsection{\textit{followingInteractions}}
\input{figures/approach/run-time-information-gathering/analysis/following-interactions.tex}

\subsubsection{Traces}
\input{figures/approach/run-time-information-gathering/analysis/traces.tex}
